Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-30 draft.tex
items on TODO list

>>>>

\section{Remark on global estimate: gradient}

\begin{remark}\label{remark:fullrecursivesum}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
    \begin{align*}
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \qquad 
        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    \end{align*}
    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
    \begin{align}\label{math:fullrecursivesum}
        \begin{split}
            \| w \|_{L^{p}(T_{m})} 
            &
            \leq 
            \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
            +
            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
            \\&
            \leq 
            A_{m} \| \nabla u \|_{L^{p}(T_{m})}
            +
            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) \left( B_{\ell+1} A_{\ell} + A'_{\ell+1} \right) \| \nabla u \|_{L^{p}(T_{\ell})}
            \\&
            =:
            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
            .
        \end{split}
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    By definition, $C_{m,0} = A_0$, and 
    \begin{align}
        C_{m,}
    \end{align}

    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \begin{split}
            \| w \|_{L^{p}(\Omega)}^{p}
            &
            \leq 
            \sum_{m=0}^{M}
            \| w \|_{L^{p}(T_{m})}^{p}
            \\&
            \leq 
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \sum_{\ell=0}^{M} 
            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
            \leq 
            \left(
                \sum_{m=0}^{M}
                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
            \right)
            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
            ,
        \end{split}
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
\end{remark}

\section{Old contraction results, now turned into a remark}

% 6. Contractible 
Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.

\color{red}
\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        \leq 
%         \left( 
%             \Cachttrafo{n}{k}{\ell}(\calT)
            % \Cacht{n}{k}(\calT)
            % \Cachtprime{n}{k}(\calT)^{k} 
            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
%             \Csiebtrafo{n}{k}{\ell}(\calT)
            % \Csieb{n}{k}(\calT)
            % \Csiebprime{n}{k}(\calT)^{k-1} 
            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
%         \right)^{M}
        \left( 
        \prod_{m=1}^{M}
            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
        \right)
        C_{{\PF},k,T_{0},p}
        \| \cartan u \|_{L^{p}(\Omega)}
        ,
    \end{align*}
    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell_{m}$ faces in common with the previous simplices.
\end{theorem}
\begin{proof}
    We prove this via induction. 
    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
    Let us assume that the statement is true for some integer $M-1 \geq 0$.

    Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
    Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
    By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
    and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star. 
    We let $\ell_{M}$ be the dimension of $S_{M}$.

    We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.

    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
    \begin{align*}
        \| g' \|_{L^{p}(\Omega')}  
        \leq 
        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
        %\Cacht{n}{k}(\calT)
        %\Cachtprime{n}{k}(\calT)^{k} 
        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
        \| g \|_{L^{p}(\Omega)}  
        .
    \end{align*}
    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
%     We have 
%     \begin{align*}
%         \| w' \|_{L^{p}(\Omega')} 
%         \leq 
%         \left( 
%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \right)^{M-1}
%         C_{{\PF},k,T_{0},p}
%         \| g' \|_{L^{p}(\Omega')}  
%     \end{align*}
    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}  
        \leq 
        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
        %\Csieb{n}{k}(\calT)
        %\Csiebprime{n}{k}(\calT)^{k-1} 
        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
        \| w' \|_{L^{p}(\Omega')} 
    \end{align*}
    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
\end{proof}
\color{black}

### 2025-01-30 main.tex
items on TODO list

% 6. Contractible 
Inspired by the contractibility of shellable triangulations, we pursue an additional estimate for Poincar\'e--Friedrichs constants. 
Every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations. 
Their bi-Lipschitz constants are controlled by the shape regularity of the domain. 
This reduces the construction of potentials over shellable triangulations to the construction of potentials over convex domains.
We refer to Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction} as the main result of this approach.

@@

\begin{remark}\label{remark:fullrecursivesum}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
    \begin{align*}
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \qquad 
        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    \end{align*}
    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
    \begin{align}\label{math:fullrecursivesum}
        \| w \|_{L^{p}(T_{m})} 
        &
        \leq 
        \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        +
        \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
        =:
        \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
        .
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}^{p}
        &
        \leq 
        \sum_{m=0}^{M}
        \| w \|_{L^{p}(T_{m})}^{p}
        % \\&
        \leq 
        \sum_{m=0}^{M}
        \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
        \sum_{\ell=0}^{M} 
        \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
        \leq 
        \left(
            \sum_{m=0}^{M}
            \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
        \right)
        \| \nabla u \|_{L^{p}(\Omega)}^{p} 
        ,
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
\end{remark}

@@

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        \leq 
%         \left( 
%             \Cachttrafo{n}{k}{\ell}(\calT)
            % \Cacht{n}{k}(\calT)
            % \Cachtprime{n}{k}(\calT)^{k} 
            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
%             \Csiebtrafo{n}{k}{\ell}(\calT)
            % \Csieb{n}{k}(\calT)
            % \Csiebprime{n}{k}(\calT)^{k-1} 
            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
%         \right)^{M}
        \left( 
        \prod_{m=1}^{M}
            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
        \right)
        C_{{\PF},k,T_{0},p}
        \| \cartan u \|_{L^{p}(\Omega)}
        ,
    \end{align*}
    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
\end{theorem}
\begin{proof}
    We prove this via induction. 
    The statement is clearly satisfied when $M=0$ because then we only consider a single simplex,
    so that the Poincar\'e--Friedrichs inequality over a simplex can be used. 
    Let us assume that the statement is true for some integer $M-1 \geq 0$.

    Recall that $X_M$ is an $n$-dimensional submanifold with boundary with a triangulation that has a shelling $T_0, T_1, \dots, T_{M-1}$. 
    Write $\Omega' \subseteq X_{M}$ for the interior domain of that manifold. 
    By Lemma~\ref{lemma:existenceofstar}, adding $T_{M}$ completes a star in $\calT$ around some simplex $S_{M} \in X_{M-1}$, 
    and we let $\Makoto_{M-1} \subseteq X_{M-1}$ be the complement of $T_{M}$ in that newly completed star. 
    We let $\ell_{M}$ be the dimension of $S_{M}$.

    We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Makoto_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
    This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Makoto_{M-1} \setminus \partial T$.
    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.

    Let $u \in W^{p}\Alt^{k}(\Omega)$ and write $g = \cartan u$. We define $g' = \Xi_{2}^{-\ast} \cartan u = \cartan \Xi_{2}^{-\ast} u$. 
    Then Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} give  
    \begin{align*}
        \| g' \|_{L^{p}(\Omega')}  
        \leq 
        \Cachttrafo{n}{k+1}{\ell_{M}}{p}(\calT)
        %\Cacht{n}{k}(\calT)
        %\Cachtprime{n}{k}(\calT)^{k} 
        %\Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
        \| g \|_{L^{p}(\Omega)}  
        .
    \end{align*}
    By induction assumption, there exists $w' \in W^{p}\Alt^{k}(\Omega')$ such that $\cartan w' = g'$.
%     We have 
%     \begin{align*}
%         \| w' \|_{L^{p}(\Omega')} 
%         \leq 
%         \left( 
%         \Cachttrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
%         \right)^{M-1}
%         C_{{\PF},k,T_{0},p}
%         \| g' \|_{L^{p}(\Omega')}  
%     \end{align*}
    Finally, $w = \Xi_{2}^{\ast} w' \in W^{p}\Alt^{k}(\Omega)$ satisfies $\cartan w = g$.
    Moreover, Proposition~\ref{proposition:pullbackestimate} and Proposition~\ref{proposition:starreflection} show 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}  
        \leq 
        \Csiebtrafo{n}{k}{\ell_{M}}{p}(\calT)
        %\Csieb{n}{k}(\calT)
        %\Csiebprime{n}{k}(\calT)^{k-1} 
        %\Cdetacht{n}{k}(\calT)^{\frac 1 p} 
        \| w' \|_{L^{p}(\Omega')} 
    \end{align*}
    We use the induction assumption to complete the estimates in the induction step is complete. The desired result follows. 
\end{proof}

@@

For the purpose of comparison, we compute reference Poincar\'e--Friedrichs constants over the reference tetrahedron via a higher-order finite element method over a mesh after three iterations of uniform refinement.
These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}.

@@

However, the results indicate significant room for improvement. 
Future estimates should tighten the gap towards the actual computed values,
including for ill-shaped simplices.

@@

We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}.
Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
allowing us to compute the best possible of these bounds.

@@

The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} and Theorem~\ref{theorem:poincarefriedrichsestimate:exterior:contraction}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\ 
        \hline
        $\calT_{C}$     & 0.3177997026 &             &                    &  1.147682616 & 3.611339490040196  \\ 
        \hline
        $\calT_{K}$     & 0.3179254398 &             &                    & 12.73827122  & 91.66905966662563  \\ 
        \hline
        $\calT_{C,5}$     &              &             &                    & 36.7821067   &                    \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C}$     & 0.2250695032 & 1.147682616 & 5.099236457042005 & 0.1837881324      & 1.5265605865      &  8.30608900893      \\ 
        \hline
        $\calT_{K}$     & 0.2250062929 & 29.14392611 & 129.5249378629681 & 0.1837655124      & 25.68030786       & 139.7449800105412   \\ 
        \hline
        $\calT_{C,5}$   &              & 160.0052039 &                   & 36.7821067        & 160.7339833       &                     \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

>>>>

@@

\begin{remark}\label{remark:fullrecursivesum}
    \color{red}
    We briefly outline how  to obtain an estimate for the Poincar\'e--Friedrichs constant from the recursive estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
    The potential $w$ for the gradient $\nabla u$ satisfies 
    \begin{align*}
        \| w \|_{L^{p}(T_{0})} \leq A_{0} \| \nabla u \|_{L^{p}(T_{0})},
        \qquad 
        % \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m} \cup T_{m-1})}                             + B_{m} \| w \|_{L^{p}(T_{m-1})},
        \| w \|_{L^{p}(T_{m})} \leq A_{m} \| \nabla u \|_{L^{p}(T_{m})} + A'_{m} \| \nabla u \|_{L^{p}(T_{m-1})} + B_{m} \| w \|_{L^{p}(T_{m-1})},
    \end{align*}
    where $A_{m}, A'_{m}, B_{m} \geq 0$ are numbers and $T_{0}, T_{1}, \dots, T_{m-1}, T_{m}$ is a face path.
    Unwrapping the recursion for the norm over the $m$-th simplex, we get a total expression of the form 
    \begin{align}\label{math:fullrecursivesum}
        \begin{split}
            \| w \|_{L^{p}(T_{m})} 
            &
            \leq 
            \sum_{\ell=0}^{m}   \left( B_{m} \cdots B_{\ell+1} \right) A_{\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
            +
            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) A'_{\ell+1} \| \nabla u \|_{L^{p}(T_{\ell})}
            \\&
            \leq 
            A_{m} \| \nabla u \|_{L^{p}(T_{m})}
            +
            \sum_{\ell=0}^{m-1} \left( B_{m} \cdots B_{\ell+2} \right) \left( B_{\ell+1} A_{\ell} + A'_{\ell+1} \right) \| \nabla u \|_{L^{p}(T_{\ell})}
            \\&
            =:
            \sum_{\ell=0}^{M} C_{m,\ell} \| \nabla u \|_{L^{p}(T_{\ell})}
            .
        \end{split}
    \end{align}
    Here, $C_{m,\ell}$ is the coefficient of $\| \nabla u \|_{L^{p}(T_{\ell})}$, possibly zero, as it appears in the unwrapped recursive estimate of $\| w \|_{L^{p}(T_{m})}$. 
    By definition, $C_{m,0} = A_0$, and 
    \begin{align}
        C_{m,}
    \end{align}

    The global Poincar\'e--Friedrichs inequality follows via H\"older's inequality:
    \begin{align*}
        \begin{split}
            \| w \|_{L^{p}(\Omega)}^{p}
            &
            \leq 
            \sum_{m=0}^{M}
            \| w \|_{L^{p}(T_{m})}^{p}
            \\&
            \leq 
            \sum_{m=0}^{M}
            \left( \sum_{\ell'=0}^{M} C_{m,\ell'}^{q} \right)^{\frac p q}
            \sum_{\ell=0}^{M} 
            \| \nabla u \|_{L^{p}(T_{\ell})}^{p} 
            \leq 
            \left(
                \sum_{m=0}^{M}
                \left( \sum_{\ell=0}^{M} C_{m,\ell}^{q} \right)^{\frac p q}
            \right)
            \| \nabla u \|_{L^{p}(\Omega)}^{p} 
            ,
        \end{split}
    \end{align*}
    where $q \in [1,\infty]$ satisfies $1 = 1/p + 1/q$ and with obvious modifications if $p=1$ or $p=\infty$. 
    In other words, the Poincar\'e--Friedrichs inequality is estimated by first taking the $q$-norm of the coefficients in the full sum~\eqref{math:fullrecursivesum} and then taking $p$-norm of these intermediate sums.
\end{remark}

@@

\begin{remark}
    As already explained in the original paper~\cite{costabel2010bogovskiui}, the operators $\Poinc_{\mia}$ preserve polynomial differential forms. 
\end{remark}

@@

\begin{remark}\label{remark:poincarefriedrichsestimate:exterior:contraction}
    We would like to point out an alternative application of Proposition~\ref{proposition:starreflection},
    using the second class of transformations. 
    Those transformations are a sequence of contractions.
    Here, we take inspiration from the topological observation that domains with shellable triangulations are contractible. 
    More specifically, we have seen that every shellable triangulation can be transformed into a single simplex along a sequence of local bi-Lipschitz deformations, and their bi-Lipschitz constants are controlled by the shape regularity of the triangulation.

    Using successive pullbacks along those contractions, the original problem of finding a potential over the domain is reduced to finding a potential for some right-hand side over the first simplex of the shelling. 
    The potential over that first simplex is then extended along successive reverse pullbacks to the whole domain. 
    Using the Poincar\'e--Friedrichs constant over the first simplex and pullback estimates (Proposition~\ref{proposition:pullbackestimate}),
    one obtains the following estimate.

    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$
    and let $0 \leq \ell_{m} < n$, for $1 \leq m \leq M$, be such that $T_{m}$ has $n - \ell_{m}$ faces in common with the previous simplices.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        \leq 
%         \left( 
%             \Cachttrafo{n}{k}{\ell}(\calT)
            % \Cacht{n}{k}(\calT)
            % \Cachtprime{n}{k}(\calT)^{k} 
            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
%             \Csiebtrafo{n}{k}{\ell}(\calT)
            % \Csieb{n}{k}(\calT)
            % \Csiebprime{n}{k}(\calT)^{k-1} 
            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
%         \right)^{M}
        \left( 
        \prod_{m=1}^{M}
            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
        \right)
        C_{{\PF},k,T_{0},p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    However, in our numerical examples (see Section~\ref{section:numericalexamples}), 
    the estimate performs significantly worse than the estimate derived in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior},
    which is why we choose to not deploy this method in our computations. 
\end{remark}

@@

For the purpose of comparison, we compute reference Poincar\'e--Friedrichs constants over the reference tetrahedron via a higher-order finite element method over a mesh after three iterations of uniform refinement.
These data are tabulated in Table~\ref{table:referencepoincarefriedrichs}. 
This example conforms to the well-known fact that the eigenvalues of the scalar Laplacian with mixed boundary conditions are between the Neumann and Dirichlet eigenvalues, which follows from a known variational principle. However, such an enclosure does not seem to hold for the vector Laplacians with mixed boundary conditions.

@@

However, the results indicate room for improvement. 
Future estimates should tighten the gap towards the actual computed values,
including for ill-shaped simplices.

@@

We compare the reference Neumann and Dirichlet eigenvalues with the bounds computed in Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}. Here, we take into account Lemma~\ref{lemma:volumecomparison} and Theorem~\ref{proposition:starreflection} (with Remark~\ref{remark:improved_starreflection}).
Again, brute-force search is feasible to enumerate all possible shellings of moderately small two-dimensional triangulations,
allowing us to compute the best possible of these bounds.

@@

The reference Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators are found via standard finite element eigenvalue computations, using the lowest-order finite element de~Rham complex over a sufficiently refined mesh (four steps of uniform refinement).
Again, we compare these reference values with estimates obtained Theorem~\ref{theorem:poincarefriedrichsestimate:exterior}, and in the special case of the gradient, with Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.

@@

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio      & $\grad$ est & $\grad$ ratio       \\ 
        \hline
        $\calT_{C}$     & 0.3177997026 &             &                    &  1.147682616 & 3.611339490040196  \\ 
        \hline
        $\calT_{K}$     & 0.3179254398 &             &                    & 12.73827122  & 91.66905966662563  \\ 
        \hline
        $\calT_{B,5}$   & 1.022627161  &             &                    & 36.7821067   & 35.96824737574127  \\ 
        \hline
        $\calT_{B}$     & 1.022627161  &             &                    & 62.40578125  & 61.02495966269372  \\ 
        \hline
        $\calT_{F}$     & 0.7117133306 &             &                    & 325.7340627  & 18796.92616132183  \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]
    \color{red}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio     & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C}$     & 0.2250695032 & 1.147682616 & 5.099236457042005 & 0.1837881324      & 1.5265605865      &  8.30608900893      \\ 
        \hline
        $\calT_{K}$     & 0.2250062929 & 29.14392611 & 129.5249378629681 & 0.1837655124      & 25.68030786       & 139.7449800105412   \\ 
        \hline
        $\calT_{B,5}$   & 0.3315710272 & 160.0052039 & 482.5669036190229 & 0.2330604743      & 160.7339833       & 689.6664212985330   \\ 
        \hline
        $\calT_{B}$     & 0.3315710272 & 572.3519405 & 1726.182004903473 & 0.2330604743      & 510.806374        & 2191.733177984011   \\ 
        \hline
        $\calT_{F}$     & 0.5549678737 & 13378.02292 & 24105.94118711908 & 0.3106774562      & 11705.58269       & 37677.60567703448   \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (3rd and 4th column) and with $k=1$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}
